Rheologic constraints on the upper mantle from five years of postseismic deformation following the El Mayor-Cucapah earthquake

### 2016-04-22 JGRSubmission/ElMayor.tex
commit before push;

\begin{keypoints}
\item = enter point 1 here = 
\item = enter point 2 here = 
\item = enter point 3 here = 
\end{keypoints}

@@

In this study, we perform a kinematic inversion for fault slip, allowing it to persist throughout the postseismic period, while simultaneously estimating the viscosity of the lower crust and upper mantle.  we use the method described in \citet{Hines2016} to create an initial model of the fault slip and effective viscosity necessary to describe early postseismic deformation, which has the richest signature of the underlying deformation mechanisms.  Our initial model describes the first 0.8 years of postseismic deformation following the El Mayor-Cucapah earthquake.  We then use the inferred effective viscosity structure from the initial model to create a suite of postseismic models to explain the five years of postseismic data available to date.  Of the suite of models tested, we find that postseismic deformation following the El Mayor-Cucapah earthquake can be explained with a combination of afterslip on a fault segment running through the Sierra Cucapah, a Zener rheology in the upper mantle with a transient viscosity that decays from $6\times10^{18}$ Pa s to $1\times10^{18}$ Pa s at 120 km depth, and a relatively stronger lower crust.

@@

\begin{figure}[h]
\includegraphics[scale=0.8]{Figures/FinalSlip}
\centering 
\caption{Inferred coseismic slip and afterslip when assuming a Maxwell rheology in the lower crust and a Zener rheology in the upper mantle.  The transient viscosity $\eta_K$ in the mantle and steady-state viscosity $\eta_M$ in the crust are set equal to the effective viscosities from Figure \ref{fig:EffectiveViscosity}. We set $\frac{\mu_K}{\mu}=0.375$ in the upper mantle.}
\label{fig:FinalSlip}
\end{figure}

>>>>

\begin{keypoints}
\item Transient postseismic deformation can be observed following the El Mayor-Cucapah earthquake at epicentral distances of up to 400 km

\item Near-field postseismic deformation exhibits early transience that decays to a sustained rate which is elevated above the preseismic trend

\item A Zener or Burgers upper mantle can explain far-field deformation while near-field transience can be described with afterslip
\end{keypoints}

@@

In this study, we perform a kinematic inversion for fault slip, allowing it to persist throughout the postseismic period, while simultaneously estimating the viscosity of the lower crust and upper mantle.  We create an initial model of the fault slip and effective viscosity necessary to describe early postseismic deformation using the method described in \citet{Hines2016}.  This method utilizes a first-order approximation of surface deformation resulting from viscoelastic relaxation which is only applicable to the early postseismic period. In this case, our initial model describes the first 0.8 years of postseismic deformation following the El Mayor-Cucapah earthquake.  We then use the inferred effective viscosity structure from the initial model to create a suite of postseismic models to explain the five years of postseismic data available to date.  Of the suite of models tested, we find that postseismic deformation following the El Mayor-Cucapah earthquake can be explained with a combination of afterslip on a fault segment running through the Sierra Cucapah and a Zener rheology in the upper mantle with a transient viscosity that decays from $6\times10^{18}$ Pa s to $1\times10^{18}$ Pa s at 120 km depth.

@@

\begin{figure}
\includegraphics[scale=0.8]{Figures/FinalSlip}
\centering 
\caption{Inferred coseismic slip and afterslip when assuming a Maxwell rheology in the lower crust and a Zener rheology in the upper mantle.  The transient viscosity $\eta_K$ in the mantle and steady-state viscosity $\eta_M$ in the crust are set equal to the effective viscosities from Figure \ref{fig:EffectiveViscosity}. We set $\frac{\mu_K}{\mu}=0.375$ in the upper mantle.}
\label{fig:FinalSlip}
\end{figure}
